\documentclass{beamer}
\usepackage{tikz}
\usetikzlibrary{shapes}
\usepackage[utf8]{inputenc}
\usetheme{Madrid}

\author[F.Paterno]{Fabio Paterno}
\title[A Theory of User-interaction Objects
]{A Theory of User-interaction Objects}
\institute[CNUCE]{Centro Nazionale Universitario di Calcolo Elettronico, Institute of CNR}
\date{\today}

\tikzstyle{oval} = [ellipse,draw,text centered]
\tikzstyle{circ} = [circle,draw,text centered]
\tikzstyle{rec} = [rectangle,draw,text centered]
\tikzstyle{dia} = [diamond,aspect=4,draw]
\tikzstyle{para} = [trapezium, trapezium left angle=70, trapezium right angle=110,draw]

\begin{document}
\maketitle

\begin{frame}{Table of Contents}
    \tableofcontents
\end{frame}

\section{Problem Definition}
\begin{frame}
\frametitle{Problem Definition}	
How to define user interface systems so that  
\begin{itemize}
	\item They can be described formally using precise mathematical notation 
	\item Their behavior and properties can be methodically evaluated
\end{itemize}
\end{frame}

\section{Motivation}
\begin{frame}
\frametitle{User Experience}
User Interfaces are an important part of the user experience. \\
They directly affect the users ability to analyze and understand the information presented. \newline \newline
But  \newline
\\They are way too complicated!
\end{frame}

\begin{frame}
\frametitle{Motivation}
Taking a mathematical approach to UI design helps us: \\
\begin{itemize}
	\item Provide useful indicators and guidelines to UI designers during design refinement phase\pause
	\item Create better automated tools for UI design and testing \pause
	\item Create more reusable UI elements
\end{itemize}
\end{frame}

\section{Previous Works}
\begin{frame}
\frametitle{Previous Works}
\addtobeamertemplate{block end}{}{\vspace*{1cm}}
\begin{block}{B. A. Myers, ACM Transactions on Information Systems 8, 289-320}
A new Model for handing input
\end{block}

\begin{block}{J. Foley et al. (1991) UIDE}
An Intelligent User interface design environment
\end{block}

\begin{block}{L. Cinque et al. (1990)}
Towards a formal specification methodology for iconic interface design
\end{block}
\end{frame}



%PART - 2 
\section{What is a UIS?}
\begin{frame}{What is a UIS?}
   	Every Application has 3 major components.
   	\begin{figure}[h]
    	\centering
    	\begin{tikzpicture}
    	\node[rec,xshift=-1cm](Application) {Application};
    	\node[rec,right of=Application,xshift=2cm](UIS) {UIS};
    	\node[rec,right of=UIS,xshift=2cm](User) {User};\pause
    	
    	\draw[->] (Application.north) -- ++(0,2) -| (UIS);
    	\draw[->] (UIS.south) -- ++(0,-2) -| (User);
    	\draw[->] (User) -- (UIS);
    	\draw[->] (UIS) -- (Application);
    	  	
    	\end{tikzpicture}
    \end{figure}
\end{frame}

\section{Building block of a UIS}
\begin{frame}{Building Block of a UIS : Interactor}
	As we can see UIS is the component that communicates between the user end and the application end.Each UIS is basically a composition of a much smaller components.\\
	 And we are calling it the \textbf{'Interactor'}   
\end{frame}

\section{Architectural Model of an Interactor}
\begin{frame}{Architectural Model of an Interactor}
	An Interactor consists of 4 architectural components.
	\begin{itemize}
		\item Measure
		\item Control
		\item Collection
		\item Presentation 
	\end{itemize}
\end{frame}
\begin{frame}
	\begin{figure}[h]
		\centering
		\begin{tikzpicture}
		
		\node[rec,minimum width = 8cm,minimum height = 5cm,xshift = 0.5cm]() {};
		\node[circ,fill=blue!35,xshift=-0.5cm,yshift = 1.35cm](Collection) {Collection};
		\node[circ,fill=green!35,xshift=-1cm,yshift=-1cm](Presentation) {Presentation};
		\node[circ,fill=yellow!35,xshift=2cm,yshift=-1cm](Measure) {Measure};
		\node[circ,fill=violet!35,xshift=2cm,yshift=1.5cm](Control) {Control};
		\node[yshift=3.5cm,xshift=0.5cm](Application) {Application Side};
		\node[yshift=-3.5cm,xshift=0.5cm](User) {User Side};\pause
		
		\draw[->] (User) -- (Measure); \pause
		\node[xshift=5cm,yshift=-1cm](TriggerUser) {Event Trigger};
		\draw[->] (TriggerUser) -- (Measure);\pause
		\draw[->] (Measure) -- (Control); \pause
		\draw[->] (Control) -- (Application);\pause
		
		\draw[->] (Application) -- (Collection);\pause
		\node[xshift=-4cm,yshift=1.35cm](TriggerApp) {Event Trigger};
		\draw[->] (TriggerApp) -- (Collection);\pause
		\draw[->] (Collection) -- (Presentation);\pause
		
		\draw[->] (Presentation) -- (User);
				
		\end{tikzpicture}
	\end{figure}
	
\end{frame}

\section{How it works?}

\begin{frame}{How it works?}
\begin{figure}[h]
	\centering
	\begin{tikzpicture}
	\node[yshift=3cm](Application) {Application Side};
	\node[yshift=-2cm](User) {User Side};
	\node[rec,minimum width = 6cm,minimum height = 2cm,yshift=0.5cm]() {};
	
	\node[xshift=2.5cm,yshift=-1.5cm](Im) {Im};\pause
	\draw[->] (Im) -- ++ (0,1);\pause
	\draw[->] (2.5,-0.35) -- ++ (0,1.5);\pause	
	\node[xshift=4.5cm,yshift=0.5cm](Bool1) {Bool};
	\draw[->] (Bool1) -- (2.6,0.5);\pause
	\draw[->] (2.5,1.4) -- ++ (0,1);\pause
	\node[xshift=2.5cm,yshift=2.6cm](Inp) {Inp};\pause
	\draw[->] (2.4,0.5) -- node[right] {If} (-1.5,0.5);\pause
	\node[rec,blue,minimum width = 2cm,minimum height = 2.5cm,xshift = 2.5cm,yshift=0.5cm](){};
	
	\node[rec,fill=blue,xshift=-5.5cm,yshift=4cm](inputFunc){};
	\node[right of=inputFunc,xshift=0.5cm](){Input Function};\pause
	% end of input behaviour
	
	
	\node[xshift=-2cm,yshift=2.6cm](Ic) {Ic};\pause
	\draw[->] (Ic) -- ++ (0,-1);\pause
	\draw[->] (-2,1.25) -- ++ (0,-1.5);\pause	
	\node[xshift=-4.5cm,yshift=0.5cm](Bool2) {Bool};
	\draw[->] (Bool2) -- (-2,0.5);\pause
	\draw[->] (-2,-0.5) -- ++ (0,-1);\pause
	\node[xshift=-2cm,yshift=-1.75cm](Out) {Out};\pause
	\node[rec,green,minimum width = 2cm,minimum height = 2.5cm,xshift = -2.5cm,yshift=0.5cm](){};
	
	\node[rec,fill=green,below of=inputFunc,yshift=0.5cm](outputFunc){};
	\node[right of=outputFunc,xshift=0.55cm](){Output Function};\pause
	
	
	
	\end{tikzpicture}

\end{figure}

\end{frame}


\section{Formal Definition of an Interactor and UIS}
\begin{frame}{Definition of an Interactor}
	
	Now, we can finally define an Interactor mathematically.
	\begin{block}{An Interactor is a pair of functions}
		$$ I = (FI,FO) $$
	\end{block}
	
	Where,\\
	
	 FI = Input Function 
	 FO = Output Function 
	
	
\end{frame}

\begin{frame}{Definition of an UIS}
So, We can define an UIS as,
\begin{block}{An UIS is a composition of of Interactors}
	$$ UIS =  \{I1,I2,I3,I4,........\}  $$
\end{block}
 
\end{frame}


\end{document}
